Pyrovelocity Notebook Usage Example

### 2024-03-29 nbs/templates/user_example/user_example.qmd
chore(nbs): sync user example with library refactor Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

```{python}
#| label: print-preprocess-data-docstring
print_docstring(pyrovelocity.preprocess.preprocess_dataset)
```

@@

The `PyrovelocityTrainInterface` is a configuration for the `pyrovelocity.train.train_dataset` function whose documentation we print below.

```{python}
#| label: print-train-model-docstring
print_docstring(pyrovelocity.train.train_dataset)
```

@@

The configuration required to postprocess the data are determined by the components of the `pyrovelocity.postprocess.postprocess_dataset` function interface whose documentation can be accessed via `help` or `?` in the notebook

```{python}
#| label: print-postprocess-data-docstring
print_docstring(pyrovelocity.postprocess.postprocess_dataset)
```

@@

```{python}
#| label: generate-marker-genes
volcano_data = posterior_samples["gene_ranking"] 
putative_marker_genes = pv.analyze.pareto_frontier_genes(volcano_data=volcano_data, num_genes=6)
```

@@

The best place to review the approach to generating the above plots is in [the source code for the `pyrovelocity.summarize` module](https://github.com/pinellolab/pyrovelocity/tree/beta/src/pyrovelocity/summarize.py) or in the [docs](https://github.io/pinellolab/pyrovelocity). Additional links are shown in the help below.

>>>>

```{python}
#| label: print-preprocess-data-docstring
print_docstring(pyrovelocity.tasks.preprocess.preprocess_dataset)
```

@@

The `PyrovelocityTrainInterface` is a configuration for the `pyrovelocity.tasks.train.train_dataset` function whose documentation we print below.

```{python}
#| label: print-train-model-docstring
print_docstring(pyrovelocity.tasks.train.train_dataset)
```

@@

The configuration required to postprocess the data are determined by the components of the `pyrovelocity.tasks.postprocess.postprocess_dataset` function interface whose documentation can be accessed via `help` or `?` in the notebook

```{python}
#| label: print-postprocess-data-docstring
print_docstring(pyrovelocity.tasks.postprocess.postprocess_dataset)
```

@@

```{python}
#| label: generate-marker-genes
volcano_data = posterior_samples["gene_ranking"] 
putative_marker_genes = pv.analysis.analyze.pareto_frontier_genes(volcano_data=volcano_data, num_genes=6)
```

@@

The best place to review the approach to generating the above plots is in [the source code for the `pyrovelocity.tasks.summarize` module](https://github.com/pinellolab/pyrovelocity/tree/beta/src/pyrovelocity/tasks/summarize.py) or in the [docs](https://github.io/pinellolab/pyrovelocity). Additional links are shown in the help below.
